\color{navyblue} Example Paper

### 2020-11-17 latex-article/article.tex
Put citations in preamble

\title{\color{navyblue} Example Paper}
% \subtitle{Subtitle}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}
% \institue{}

\input{preamble.tex}

% Set-up Bibliography ------------------------------
\usepackage[
    citestyle= authoryear,
    style= authoryear, 
    natbib= true, 
    backend= biber
]{biblatex}
\addbibresource{references.bib}

@@

See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citep{Eigen1971}.

>>>>

\title{\color{navyblue} Example Paper}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

% Include Theme
\input{preamble.tex}

% Set-up Bibliography
\addbibresource{references.bib}

@@

See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citet{Eigen1971}.
